On the presentation of orthogonal groups over polynomial rings

### 2019-05-26 dl-paper.tex
Minor fixes

\begin{corollary} \label{Kgen-strong} For $A$ and $M$ as in~\cref{thmStein} and arbitrary fixed root $\gamma$ of an irreducible simply-laced root system $\Phi$ the subgroup $K(A[X], M[X])$ is generated as a group by $\overline{\St}(\Phi, A[X], XM[X])$ and the elements $c_{\gamma}(m, X\eta)$, where $m \in M$, $\eta \in A[X]$. \end{corollary}
\begin{proof} Substituting $\xi = 1$, $s = m$, $t = X\eta$ into relation~\eqref{C4} of~\cref{Crels} we obtain that modulo 
 $\overline{\St}(\Phi, A[X], XM[X])$ the element $c_{\alpha + \beta}(m, X\eta)$ is equivalent to $c_{\alpha}(-\epsilon m, -\epsilon X \eta)^{-1}$, $\epsilon = N_{\alpha, \beta}$. The assertion of the corollary now easily follows from the irreducibility of $\Phi$.
\end{proof}

@@

\subsection{The subgroups \texorpdfstring{$K(\alpha, \beta)$}{K(a,b)} and their properties}
Throughout this subsection $\alpha, \beta$ denote a fixed pair of roots of $\Phi$ forming a sharp angle (i.\,e. $\langle \alpha, \beta \rangle = 1$). We denote by $\Psi$ the subsystem of type $\rA_2$ generated by $\alpha$ and $\beta$.
\begin{df} Denote by $K(\alpha, \beta)$ the subgroup of $\St(\Phi, A[X, X^{-1}])$ generated by the following elements:
 \begin{enumerate}
  \item $z_\gamma(Xf, \xi)$, for all $\gamma \in \Phi \setminus \Psi$;
  \item $x_{-\alpha}(X^2f)$, $x_{-\beta}(X^2f)$;
  \item $x_{\alpha}(Xf)$, $x_\beta(Xf)$;
  \item $x_{\alpha-\beta}(Xf)$, $x_{\beta-\alpha}(Xf)$;
  \item $c_{\delta}(f, X\xi)$ for some fixed root $\delta \in \Phi \setminus \Psi$. \end{enumerate} \end{df}

@@

\begin{lemma} Let $\Phi$ be a simply-laced root system of rank $\geq 3$, $(A, M)$ be a local pair. Then for $\alpha \in \Phi$ the partial function $t_\alpha(aX^{-1}) \colon V \not \to V$ descends to a well-defined total function 
  $T_\alpha(aX^{-1}) \colon \overline{V} \to \overline{V}$. \end{lemma}
\begin{proof}
 First of all, let us show that the resulting function is total. 
 Fix $(g, h, u) \in V$. Since $p(g, h, u) \in \overline{G}^{\geq 0}_M$ there exists $g_1 \in \overline{\St}(\Phi, A[X], M[X])$ such that $j_+(g_1) = p(g, h, u).$
 Set $h_0 = ev^*_{X=0}(g_1)^{-1}$, then, clearly, $g_1 \cdot i_+(h_0) \in K(A[X], M[X])$ and 
 $p(g, h \cdot i_-(h_0), u) = j_+(g_1) \cdot j_-(i_-(h_0)) = j_+(g_1 \cdot i_+(h_0)) \in j_+(K(A[X], M[X])) \subseteq P_\alpha(*)$,
  which shows that $t_\alpha(aX^{-1})$ is defined on $(g, h \cdot i_+(h_0), u)$, which is also a representative of the same orbit as $(g, h, u)$.

@@

\begin{comment}
The next step of the proof is to pass from the set $V_0'$ to its quotient $V_0$ 
We allow multiplying the second component on the right by an element of $\mathrm{im}(\St(\Phi, A, M) \to \St(\Phi, A))$
 (this operation is well defined for $V'_0$).

@@

\begin{align*} x_{\alpha+\beta+\gamma}(abX^{-1}) = {}^{x_{-\beta}(X^{-1})}\!x_{\alpha+\beta+\gamma}(abX^{-1}) & \text{ by the above relation}\\
 = {}^{x_{-\beta}(X^{-1})}\![x_{\alpha+\beta}(b'), x_\gamma(aX^{-1})] & \text{ by R$2_1$} \\
 = [x_{\alpha}(b'X^{-1}) x_{\alpha+\beta}(b'), x_\gamma(aX^{-1})] & \text{ by R$2_1$ and R$3_1$ for sharp angles }\\
 = {}^{x_{\alpha}(b'X^{-1})}\!x_{\alpha+\beta+\gamma}(abX^{-1}) [x_{\alpha}(b'X^{-1}), x_\gamma(aX^{-1})] & \text{ by R$2_1$} \\
 = x_{\alpha+\beta+\gamma}(abX^{-1}) [x_{\alpha}(b'X^{-1}), x_\gamma(aX^{-1})] & \text{ by R$3_1$ for sharp angles.} \end{align*}
\end{comment}
\printbibliography
\end{document}

>>>>

\begin{corollary} \label{Kgen-strong} For a local pair $(A, M)$ and arbitrary fixed root $\gamma$ of an irreducible simply-laced root system $\Phi$ the subgroup $K(A[X], M[X])$ is generated as a group by $\overline{\St}(\Phi, A[X], XM[X])$ and the elements $c_{\gamma}(m, X\eta)$, where $m \in M$, $\eta \in A[X]$. \end{corollary}
\begin{proof} Substituting $\xi = 1$, $s = m$, $t = X\eta$ into relation~\eqref{C4} of~\cref{Crels} we obtain that modulo 
 $\overline{\St}(\Phi, A[X], XM[X])$ the element $c_{\alpha + \beta}(m, X\eta)$ is equivalent to $c_{\alpha}(-\epsilon m, -\epsilon X \eta)^{-1}$, $\epsilon = N_{\alpha, \beta}$. The assertion of the corollary now easily follows from the irreducibility of $\Phi$.
\end{proof}

@@

\subsection{The subgroups \texorpdfstring{$K(\alpha, \beta)$}{K(a,b)} and their properties}
Throughout this subsection $\alpha, \beta$ denote a fixed pair of roots of $\Phi$ forming a sharp angle (i.\,e. $\langle \alpha, \beta \rangle = 1$). We denote by $\Psi$ the subsystem of type $\rA_2$ generated by $\alpha$ and $\beta$.
\begin{df} Denote by $K(\alpha, \beta)$ the subgroup of $\St(\Phi, A[X, X^{-1}])$ generated by the following elements:
 \begin{enumerate}
  \item $z_\gamma(Xf, \xi)$, for all $\gamma \in \Phi \setminus \Psi$;
  \item $x_{-\alpha}(X^2f)$, $x_{-\beta}(X^2f)$;
  \item $x_{\alpha}(Xf)$, $x_\beta(Xf)$;
  \item $x_{\alpha-\beta}(Xf)$, $x_{\beta-\alpha}(Xf)$;
  \item $c_{\delta}(f, X\xi)$ for some fixed root $\delta \in \Phi \setminus \Psi$. \end{enumerate} \end{df}
Notice that a priori $K(\alpha, \beta)$ depends on a choice of $\delta$, however as the next proposition shows, there is no such dependence.

@@

\begin{lemma} Let $\Phi$ be a simply-laced root system of rank $\geq 3$ and $(A, M)$ be a local pair. Then for $\alpha \in \Phi$ the partial function $t_\alpha(aX^{-1}) \colon V \not \to V$ descends to a well-defined total function 
  $T_\alpha(aX^{-1}) \colon \overline{V} \to \overline{V}$. \end{lemma}
\begin{proof}
 First of all, let us show that the resulting function is total. 
 Fix $(g, h, u) \in V$. Since $p(g, h, u) \in \overline{G}^{\geq 0}_M$ there exists $g_1 \in \overline{\St}(\Phi, A[X], M[X])$ such that $j_+(g_1) = p(g, h, u).$
 Set $h_0 = ev^*_{X=0}(g_1)^{-1}$, then, clearly, $g_1 \cdot i_+(h_0) \in K(A[X], M[X])$ and 
 $p(g, h \cdot i_-(h_0), u) = j_+(g_1) \cdot j_-(i_-(h_0)) = j_+(g_1 \cdot i_+(h_0)) \in j_+(K(A[X], M[X])) \subseteq P_\alpha(*)$,
  which shows that $t_\alpha(aX^{-1})$ is defined on $(g, h \cdot i_+(h_0), u)$, which is also a representative of the same orbit as $(g, h, u)$.

@@

The next step of the proof is to pass from the set $V_0'$ to its quotient $V_0$ 
We allow multiplying the second component on the right by an element of $\mathrm{im}(\St(\Phi, A, M) \to \St(\Phi, A))$
 (this operation is well defined for $V'_0$).

@@

\begin{align*} x_{\alpha+\beta+\gamma}(abX^{-1}) = {}^{x_{-\beta}(X^{-1})}\!x_{\alpha+\beta+\gamma}(abX^{-1}) & \text{ by the above relation}\\
 = {}^{x_{-\beta}(X^{-1})}\![x_{\alpha+\beta}(b'), x_\gamma(aX^{-1})] & \text{ by R$2_1$} \\
 = [x_{\alpha}(b'X^{-1}) x_{\alpha+\beta}(b'), x_\gamma(aX^{-1})] & \text{ by R$2_1$ and R$3_1$ for sharp angles }\\
 = {}^{x_{\alpha}(b'X^{-1})}\!x_{\alpha+\beta+\gamma}(abX^{-1}) [x_{\alpha}(b'X^{-1}), x_\gamma(aX^{-1})] & \text{ by R$2_1$} \\
 = x_{\alpha+\beta+\gamma}(abX^{-1}) [x_{\alpha}(b'X^{-1}), x_\gamma(aX^{-1})] & \text{ by R$3_1$ for sharp angles.} \end{align*}

\include{rehmann}

\printbibliography

\end{document}
